%% This layout has been constructed from the combination of several packages, layout found on internet and from my own construction. 
%% It is done to match the layout of Centrale Méditerranée but can be adapted for other university
%% Author: Vincent G. 2025 (Promo Entrante 2022)


\documentclass[11pt]{memoir}

% Front page (Replace with your own information)
\newcommand{\prenomNOM}{ZHAO Chao} % prénom NOM
\newcommand{\dateDebutStage}{01/04/2025} % jour/mois/année
\newcommand{\dateFinStage}{01/10/2025} % jour/mois/année
\newcommand{\nomEntreprise}{École nationale des ponts et chaussées} % Nom de l'entreprise 
\newcommand{\sujetMission}{DigiEV: A digital twin for electric vehicle charging
infrastructure in the E4C ecosystem} % Sujet de mission 
\newcommand{\supervisor}{Dr.Daphne Tuncer (École des ponts)}
\newcommand{\cosupervisor}{Dr.Georgios Bouloukakis (Télécom SudParis)}
\newcommand{\attestation}{
  \vskip 0.5em
  \justifying
  Je, soussignée Daphne Tuncer, maître de stage de l'élève Isep, ZHAO Chao, atteste avoir pris connaissance du
  cahier des charges du rapport de stage Isep, avoir lu et évalué le présent rapport au regard
  du cahier des charges et des pratiques de mon employeur, et autorisée sa transmission à l'Isep.
  \vskip 0.5em
  \hfill Signature / Date :
}





\setlength{\headheight}{14.80524pt}
\input{MainLayout/Packages}
\input{MainLayout/PageLayout}

\input{MainLayout/ChapterStyle}

\makeatother


\chapterstyle{HansenColor}

\begin{document}

\setcounter{secnumdepth}{3}
\thispagestyle{empty}
\include{MainLayout/TitlePage}

\newgeometry{top=3cm, bottom=1cm, left=2cm, right=6cm}  % set new margins


% --- Remerciements ---
\chapter*{Acknowledgments}

I would like to sincerely thank my supervision team, Dr.Daphne Tuncer and Dr.Georgios Bouloukakis, for their continuous guidance, insightful advice, and encouragement throughout this six-month internship. Their expertise not only supported my R\&D tasks but also inspired me to explore the world of academic research, opening a new path in my professional journey.

I am also deeply grateful to my wife, WANG Yaoyao, for her unconditional support in daily life. Her encouragement has been a vital source of strength during this period. In addition, I would like to express my heartfelt gratitude to my parents, whose love, trust, and support have always been the foundation of my personal and professional growth. All their constant encouragement has given me the confidence to pursue new challenges and persist through difficulties.

Lastly, I would like to acknowledge E4C for providing the resources and support that made this internship possible.


% \bigskip
% % \begin{center}
% %     \Huge * * *
% % \end{center}

\newpage


% --- Abstract ---

\chapter*{Abstract}
% ENGLISH ABSTRACT

The success of electric mobility requires not only advanced electric vehicles but also an integrated infrastructure that combines electricity provision, information distribution, and intelligent system control. Digital twin technology has emerged as a powerful approach to manage complex infrastructure operations and evaluate deployment strategies for electric vehicle charging networks.

This report describes the work conducted during my six-month internship at Laboratoire Ville Mobilité Transport (LVMT), focusing on the design and development of a digital twin system to simulate the energy impact of electric vehicle charging infrastructure. The project employed FIWARE technology as the core framework, utilizing Python for system development and data processing to model the complex interactions between energy consumption and user behavior in charging station.

The developed digital twin system successfully established a comprehensive platform for simulating charging station operations, built upon NGSI-LD standard compliance to ensure semantic interoperability. The system utilizes MongoDB and CrateDB as backend databases for efficient data storage and time-series analysis, while providing RESTful API interfaces for seamless system integration and external interactions. This platform enables real-time monitoring and analysis of charging infrastructure performance, providing valuable insights for optimizing charging station deployment, predicting energy demand patterns, and improving overall system efficiency. The work contributes to enhanced decision-making capabilities for electric vehicle charging infrastructure planning and management through standardized data models and accessible programming interfaces.

This internship significantly enhanced my technical expertise. Additionally, I strengthened my research skills through extensive literature review and analysis of current challenges in sustainable transportation infrastructure. The experience provided valuable insights into the interdisciplinary nature of smart city technologies and the critical role of digital twins in managing complex urban systems.

\bigskip\bigskip

\textbf{\color{CentraleBlue}Keywords} Digital Twin, Simulator, Semantic Model, Electric Vehicle, Charging Infrastructure, FIWARE

\newpage

\restoregeometry 

\tableofcontents

%%% Chapters %%%
\include{Chapters/Chapter1}
\include{Chapters/Chapter2}


%%% Glossaire %%%
\printglossaries


%%% Appendix %%%
\appendix

\include{Chapters/Appendix/Appendix1}


\urlstyle{same}


%%% Bibliography %%%
\bibliographystyle{plain} 
\bibliography{References}

\end{document}

